Improved Global Routing By Using A Star Algorithm

### 2020-06-01 paper.tex
Second Related Work Paper

Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some papers tried to decrease the number of vias, other papers tried to decrease the time taken and so on.
\par
In \cite{b1} a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR. optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps. First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded. Second, if the route started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path. Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing. Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wirelength is enough to detour around congested regions. The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR). But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
\par
In \cite{b4}

@@

>>>>

Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some papers tried to decrease the number of vias, other papers tried to decrease the time taken and so on.
\par
In \cite{b1} a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR. optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps. First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded. Second, if the route started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path. Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing. Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wirelength is enough to detour around congested regions. The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR). But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
\par
In \cite{b4}, both of via count and runtime are reduced, this done by integrating \cite{b10}, \cite{b11}, and \cite{b12} with via aware Steiner tree generation, 3-bend routing, and layer assignment with careful edge and net ordering to create \cite{b4}. Via aware Steiner tree is used to at the beginning of the global routing, it generates a suitable topology, by changing tree topology the via count greatly changed, which means that using a suitable topology for Steiner tree will greatly reduce the via count. The 3-bend routing is used instead of L, U, Z, maze, and monotonic routing, as L, U, Z routing can not avoid congestions but they generate a little number of vias, maze and monotonic can avoid congestions but they generate a lot of vias and their runtime is very high, so the 3-bend routing was used as it is fast, its completely \textit{O(nm)}, and it generates vias less than maze and monotonic routing as it consists of two L routing. Layer assignment with careful ordering algorithm is used as a solution of \textit{3D}, it is like all the modern techniques projects the \textit{3D} grid into \textit{2D} one to be easier and faster in routing, this algorithm guarantees the wirelength and overflow unchanged on assigning to layers, dynamic programming is used in layer assignment to make it faster. From the previous explanation the advantages of this paper are decreasing number of vias, which means less power consumption and circuit delay, and decreasing runtime of global routing thus decreasing runtime of whole the routing process. But it has disadvantages too, one of them is the wirelength is not optimal, as using 3-bend routing increases the wirelength to avoid congestions, another one is caused by layer assignment, as if the \textit{2D} was not congestion-free the results will not be accurate.

@@

    \bibitem{b10} Zhang, Yanheng, Yue Xu, and Chris Chu. "FastRoute3. 0: a fast and high quality global router based on virtual capacity." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.} IEEE, 2008.

    \bibitem{b11} Pan, Min, and Chris Chu. "FastRoute: A step to integrate global routing into placement." \textit{Proceedings of the 2006 IEEE/ACM international conference on Computer-aided design.} 2006.

    \bibitem{b12} Pan, Min, and Chris Chu. "FastRoute 2.0: A high-quality and efficient global router." \textit{2007 Asia and south pacific design automation conference.} IEEE, 2007.
